### 2013-10-16 articles/Proposal-wsclean/paper-proposal-fast-widefield-imager.tex

\label{firstpage}
\section*{MWA paper proposal: ``WSClean: a new implementation of a fast, generic wide-field imager''}
\begin{tabular}{ll}
Publication title: & WSClean: a new implementation of a fast, generic \\
                   & wide-field imager\\
                   & \\
Principle contact: & Dr. Andr\'e R. Offringa \\
                   & \\
Draft publication        & A.~R.~Offringa, B.~McKinley, N.~Hurley-Walker, \\
\hspace{5mm}author list: & F.~H.~Briggs, J. Rhee, MWA commissioning team \\
                         & and GLEAM members where appropriate, MWA \\
                         & builders list \\
                   & \\
Journal:           & Probably MNRAS\\
                   & \\
Intended date of submission\\
\hspace{5mm}to collaboration: & February 2014\\
\end{tabular}

>>>>

\label{firstpage}
\section*{MWA paper proposal: ``WSClean: a new implementation of a fast, generic wide-field imager''}
\begin{tabular}{ll}
Publication title: & WSClean: a new implementation of a fast, generic \\
                   & wide-field imager\\
                   & \\
Principle contact: & Dr. Andr\'e R. Offringa \\
                   & \\
Draft publication        & A.~R.~Offringa, B.~McKinley, N.~Hurley-Walker, \\
\hspace{5mm}author list: & F.~H.~Briggs, J.~Rhee, L.~Feng, D.~Kaplan, \\
                         & A.~R.~Neben, MWA commissioning team \\
                         & and GLEAM members where appropriate, MWA \\
                         & builders list \\
                   & \\
Journal:           & Probably MNRAS\\
                   & \\
Intended date of submission\\
\hspace{5mm}to collaboration: & February 2014\\
\end{tabular}
